Spec2Fab: A Graph-Based Framework for Fabricating Fabrication Algorithms

### 2012-12-21 paper.tex
pseudo code

\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{hyperref}
\title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}

@@

 See \textbf{Figure \ref{fig:red1}} for an example of a Reducer Network. \note{Desai: Make figure 1}.

@@

>>>>

\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{program}
\title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}

@@

 See \textbf{Figure \ref{fig:red1}} for an example of a Reducer Network. \note{Desai: Make figure 1}.\\
The sample Reducer Network can be constructed with the following pseudo-code.
%There are may be a better place to put the pseudo code
%\begin{program} can't figure out how to put it into a box
\begin{verbatim}
stratum->addInput(inputNode,0);
column->addInput(stratum, 0);
//add layered material to each column
for(ii =0;ii<column->getNOutput();ii++){
  layer = new LayeredMaterial(2);
  layer->addInput(column,ii);
}
uniform = new UniformMaterial(0);
uniform->addInput(stratum,1);
\end{verbatim}
%\caption{The Hello World! program in Java.}
%\end{program}

@@

The Tuner graph can be constructed using the following pseudo-code
%Can't figure out how to put it into a box
\begin{verbatim}
for(ii=0;ii<column->resolution;ii++){
  for(jj =0;jj<column->resolution;jj++){
  //add 4 neighbors for each tuner
      tuner[ii][jj].nbr.push_back(ii,jj+1);
      tuner[ii][jj].nbr.push_back(ii+1,jj-1);
      tuner[ii][jj].nbr.push_back(ii+1,jj);
      tuner[ii][jj].nbr.push_back(ii+1,jj+1);    
    }
  }
}
\end{verbatim}
